A Gentle Introduction and Application of Feature-Based Clustering with Psychological Time Series

### 2023-07-29 sections/03FeatureExtraction.Rmd
writing adj.

<!--Effective degrees of freedom for individual smooth terms are obtained by summing the Fii values corresponding to the coefficients βi of the smooth term (e.g., if the coefficients of a particular smooth are β5, . . . , β11 then the smooth’s EDF is $\sum_{i=5}^{11} = F_{ii}).--!>

<!-- An alternative approach to understanding the edf is to approximate the number of parametric and non-parametric (or smooth) terms $p$ in the penalized GAM. Both formulas are measuring the same concept (the model's complexity or flexibility) and both account for the penalization introduced to control overfitting in GAMs \citep{hastie1986}.

```{=tex}
\begin{equation} \label{eq:edf}
  edf \approx \sum p
\end{equation}
```
--!>

>>>>

```{r}
#| include: False

# Effective degrees of freedom for individual smooth terms are obtained by summing the Fii values corresponding to the coefficients βi of the smooth term (e.g., if the coefficients of a particular smooth are β5, . . . , β11 then the smooth’s EDF is $\sum_{i=5}^{11} = F_{ii}).
# 
# An alternative approach to understanding the edf is to approximate the number of parametric and non-parametric (or smooth) terms $p$ in the penalized GAM. Both formulas are measuring the same concept (the model's complexity or flexibility) and both account for the penalization introduced to control overfitting in GAMs \citep{hastie1986}.
# 
# ```{=tex}
# \begin{equation} \label{eq:edf}
#   edf \approx \sum p
# \end{equation}
# ```
```
